%-------------------------
% Resume in Latex
% Author : Matt Aquino
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Matt Aquino} \\ \vspace{1pt}
    Toronto, Ontario \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 289-221-9227 ~ \href{mailto:matthew@aquino.lol}{\raisebox{-0.2\height}\faEnvelope\  \underline{matthew@aquino.lol}} ~ 
    \href{https://www.linkedin.com/in/matthew-aquino-/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/matthew-aquino-/}}  ~
    \href{https://github.com/MatthewAquino}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/MatthewAquino}}
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google }{October 2022 -- Present}
      {Solutions Consultant}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Drive the successful adoption of Google Cloud, managing implementation efforts, offering technical expertise, and overseeing project timelines, resulting in a 97\% rating in an annual customer satisfaction survey.}
        \resumeItem{Lead a team of 5 Technical Account Managers, overseeing the creation of onboarding materials and training curriculum reducing the time needed for to onboard new TAMs by 1 week.}
        \resumeItem{Reduced customer escalation rate by 15\% over one year by developing standard operating procedures (SOPs) on how customers best engage with our support organization.}
        \resumeItem{Achieved a 95\% customer satisfaction score in 2023 by cultivating strong relationships with assigned customers and positioning myself as a trusted advisor.}
        \resumeItem{Lead several training sessions with media customers on Google Clouds Generative AI offerings, resulting in the launch of the first media AI use case to approximately 15 million users}
      \resumeItemListEnd

    \resumeSubheading
      {Tanium}{March 2021 -- October 2022}
      {Associate, Technical Account Manager}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Served as the primary technical point of contact for financial and government customers. Managing a book of business of ~ \$25 million }
        \resumeItem{Acted as the key technical liaison for customers, gathering and analyzing their feedback and requirements to inform product development and road-map decisions, resulting in a 20\% increase in customer satisfaction.}
        \resumeItem{Led a program to create a set of regular actives to be run with customers every quarter, Account teams that used these saw on average 17\% increase of yearly revenue}
    \resumeItemListEnd

    \resumeSubheading
      {The ITM Group}{June 2020 -- March 2021}
      {Cloud Architect}{Toronto, Ontario}
      \resumeItemListStart
        \resumeItem{Initiated a cloud-first strategy, leading the successful migration of critical systems and applications to Azure. This effort resulted in enhanced scalability, redundancy, and the achievement of a 99.99\% Uptime SLA.}
        \resumeItem{Designed and implemented cost-effective cloud infrastructure, aligning it with organizational requirements. This transition from on-premises systems led to annual cost savings of approximately \$65,000.}
        \resumeItem{ Developed automation workflows in Powershell and Python, reducing the time required to complete common tasks by up to 50\%. }
    \resumeItemListEnd

    \resumeSubheading
      {The ITM Group}{January 2020 -- June 2020}
      {System/Network Administrator}{Toronto, Ontario}
       \resumeItemListStart
        \resumeItem{Partnered with systems teams to assist with the building, configuring, patching, upgrading and troubleshooting of physical and virtual Windows and Linux servers.}
        \resumeItem{Managed the system and networking infrastructure of a data center that hosts 300+ servers and hosts services for 20 companies.}
        \resumeItem{Acted as a level 3 escalation point for complex networking and operating system issues. Resolving 50 tickets per week}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgian College}{Aug. 2018 -- May 2021}
      {College Diploma : Computer Systems Technician - Networking}{Barrie, Ontario}
  \resumeSubHeadingListEnd

%-----------Certifications---------------
\section{Certifications}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Google Cloud: }{Associate Cloud Engineer} \\ \vspace{3pt}

        \textbf{Google Cloud: }{Professional Workspace Administrator} \\ \vspace{3pt}

        \textbf{Google Cloud: }{Professional Cloud Architect} \\ \vspace{3pt}
    
        \textbf{Microsoft Azure:} {Certified Azure Fundamentals} \\ \vspace{3pt}
        
        \textbf{Amazon Web Services:} {Certified Cloud Practitioner} \\ \vspace{3pt}


    }}
  \resumeSubHeadingListEnd

\end{document}